---
title: "COVID-19 Outbreaks in Healthcare Institutions"
author: "ruihan zhang"
date: 2020-09-26T21:13:14-05:00
bibliography: "references.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---
# Author: Ruihan Zhang
```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```
# Abstraction
During COVID-19, healthcare institutions are the first line of the epidemic outbreaks. In order to help these healthcare institutions to prepare better in epidemic prevention, my goal is to find the most regular continued time for COVID_19 outbreaks. In addition, I want to find the type of healthcare institutions that outbreaks most possible to happen.

# Introduction
This dataset is about the outbreaks in Toronto healthcare institutions
(including hospitals, long-term care homes and retirement homes). 

These healthcare institutions have the responsibility to monitor staff 
and patients/residents for signs and symptoms of gastroenteric and respiratory
such as nausea, vomiting, diarrhea, fever, cough, runny nose and sore throat.

If the rate of infection or illness increase locally or higher than expectation,we call it "outbreak".

In this study, I want to find out the regular continued time of the outbreaks in these healthcare institutions, and which type of institutions is most possible to have outbreaks.

I use @citetidyverse, @citeopendatatoronto， @citedplyr.

# Data discussion
Here is the introduction for the variables I observed.

Outbreak setting: The type of healthcare institutions provided and have outbreaks.

Type of outbreak: Classification and description of outbreaks transmission mode.

Causative agent-1: Because we want to discuss about COVID-19, I removed the data excluding COVID-19.

Time: The time of outbreaks last.

I removed some variables from the original data, and here is the reasons I removed them:

Causative Agent - 2: There are too many missing data in this variables

Date Outbreak Began and Date Declared Over:
I calculate the difference between the over date and the start date, such that I removed the start and over time for the outbreaks.

Active: 'Active' shows the status of outbreaks due on the report date. If the outbreaks still active on the due date, it is meanless to study on the length of time for the outbreaks. Such that I removed the data that show 'yes' in the 'Active' variable first. Since rest of 'Active' are all 'no', I delete this variable.

# Code part

```{r outbreak}
install.packages("opendatatoronto")
library(opendatatoronto)
library(dplyr)

library(tidyverse)
# get package
package <- show_package("80ce0bd7-adb2-4568-b9d7-712f6ba38e4e")
package

resources <- list_package_resources("80ce0bd7-adb2-4568-b9d7-712f6ba38e4e")
datastore_resources <- filter(resources, tolower(format)%in%c('xlsx','ob_report_2020'))

data <- filter(datastore_resources,row_number()==2) %>% get_resource()
data


colSums(is.na(data))

data1 = data %>%
  select(-`Causative Agent - 2`)

data1 = data1[data1$`Causative Agent - 1` %in% c('COVID-19'),]


data1$`time` = difftime(data1$`Date Declared Over`,data1$`Date Outbreak Began`,units="days")


data1 = data1 %>%
  select(-`Institution Address`)

data1 = data1[!data1$Active %in% c('Y'),]

data1 = data1 %>%
  select(-Active)

data1 = data1 %>%
  select(-`Date Outbreak Began`, -`Date Declared Over`)


data1$`Outbreak Setting` <- ifelse(data1$`Outbreak Setting` == 'Hospital-Acute Care',  1, data1$`Outbreak Setting`);
data1$`Outbreak Setting` <- ifelse(data1$`Outbreak Setting` == 'Hospital-Psychiatric',  2, data1$`Outbreak Setting`);
data1$`Outbreak Setting` <- ifelse(data1$`Outbreak Setting` == 'LTCH',  3, data1$`Outbreak Setting`);
data1$`Outbreak Setting` <- ifelse(data1$`Outbreak Setting` == 'Retirement Home',  4, data1$`Outbreak Setting`);
data1$`Outbreak Setting` <- ifelse(data1$`Outbreak Setting` == 'Hospital-Chronic Care',  5, data1$`Outbreak Setting`);

# Graph
ggplot(data = data1,aes(x = `time`)) + 
  geom_histogram(color='grey', fill='purple',bins= 10)

ggplot(data = data1,aes(x = `Outbreak Setting`)) + 
  stat_count(color='white', fill='pink')

```

# Graph Discussion
From the plot of the time and count, I found that for most institutions the last time of COVID-19 outbreaks is two weeks.

And the number of outbreaks happened in long-term care homes is obviously greater than any other type of healthcare institutions. This maybe because the patients in the long-term care homes are mostly elder people with Poor physical condition. This leads to the poor immunity for the patients. Therefore, this type of healthcare institutions have highier proportion in outbreaks.

Therefore, we can pay more attention to protect the in long-term care homes from COVID-19, and we know that the best isolation period is longer than two weeks.

# Reference
https://open.toronto.ca/dataset/outbreaks-in-toronto-healthcare-institutions/
